\documentclass{article}
\usepackage[english]{babel}
\usepackage{geometry,amssymb,enumerate,theorem,amsmath}
\geometry{a4paper, bottom=20mm, top=20mm}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\TeXmacs}{T\kern-.1667em\lower.5ex\hbox{E}\kern-.125emX\kern-.1em\lower.5ex\hbox{\textsc{m\kern-.05ema\kern-.125emc\kern-.05ems}}}
\newcommand{\mathd}{\mathrm{d}}
\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
\newenvironment{enumeratealpha}{\begin{enumerate}[a{\textup{)}}] }{\end{enumerate}}
{\theorembodyfont{\rmfamily\small}\newtheorem{exercise}{Exercise}}
%%%%%%%%%% End TeXmacs macros

\newcommand{\renderexercise}[2]{{\paddednormal{0.5fn}{0.5fn}{{\exercisename{#1{\exercisesep}}}#2}}}

\begin{document}

\setlength{\parindent}{0cm}{\small{\tmtextbf{Institute for Applied Mathematics
-- SS2020}}}\hspace{4cm}\hbox{}

{\small{Massimiliano Gubinelli}}

\


{\center{{\LARGE{\tmtextbf{V4F1 Stochastic Analysis -- Problem Sheet 2}}}

\ }}


{\scriptsize{Version 2. Tutorial classes: Mon May 11th 16--18 \ (Zoom) Min Liu
\textbar  Wed May 13th 16--18 (Zoom) Daria Frolova.

Solutions in groups of 2 (at most). To be handled in {\LaTeX} or {\TeXmacs}
format via eCampus not later than 4pm Thursday May 7th. Use this sheet for
your solutions and write them under the corresponding exercise. Fill out your
names below.

\ }}

\tmtextbf{Names: XXXXXXXXXXXX/YYYYYYYYYYYYYY}

\

\

\hrulefill

\begin{exercise}
  [Pts 2+3+2] Let $(B_t)_{t \geqslant 0}$ be a one dimensional Brownian
  motion.
  \begin{enumeratealpha}
    \item Define the process
    \[ X_t = a (t) \left( x_0 + \int_0^t b (s) \mathd B_s \right) \]
    where $a, b : \mathbb{R}_+ \rightarrow \mathbb{R}$ are differentiable
    functions with $a (0) = 1$ and $a (t) > 0$. Compute the SDE satisfied by
    this process.
    
    \item Use (a) to find an explicit solution for the SDEs in
    eqns.{\eqref{eq:sde1}}, {\eqref{eq:sde2}}, {\eqref{eq:sde3}}:
    \begin{equation}
      \left\{\begin{array}{lll}
        \mathd X_t & = & - \alpha X_t \mathd t + \sigma \mathd B_t \qquad t
        \in [0, T]\\
        X_0 & = & x_0
      \end{array}\right. \label{eq:sde1}
    \end{equation}
    where $\alpha, \sigma, T$ are positive constants.
    \begin{equation}
      \left\{\begin{array}{lll}
        \mathd X_t & = & - \frac{X_t}{1 - t} \mathd t + \mathd B_t \qquad t
        \in [0, 1)\\
        X_0 & = & 0
      \end{array}\right. \label{eq:sde2}
    \end{equation}
    \begin{equation}
      \left\{\begin{array}{lll}
        \mathd X_t & = & t X_t \mathd t + e^{t^2 / 2} \mathd B_t \qquad t \in
        [0, T]\\
        X_0 & = & 1
      \end{array}\right. \label{eq:sde3}
    \end{equation}
    \item Are the solutions of the SDEs in (b) strong and pathwise unique?
  \end{enumeratealpha}
\end{exercise}

\

\begin{exercise}
  [Pts 2+2+2] Let $(B_t)_{t \geqslant 0}$ be a one dimensional Brownian
  motion.
  \begin{enumeratealpha}
    \item Given $f \in C (\mathbb{R}_+)$, prove that $X_t = \int_0^t f (s)
    \mathd B_s$ is a Gaussian random variable with mean $0$ and variance
    $\int_0^t f (u)^2 \mathd u$ for all\quad$t \geqslant 0$.
    
    \item The Ornstein--Uhlenbeck process $(X_t)_{t \geqslant 0}$ is defined
    as the solution to the SDE
    \begin{equation}
      \left\{\begin{array}{lll}
        \mathd X_t & = & (- \alpha X_t + \beta) \mathd t + \sigma \mathd B_t
        \qquad t \geqslant 0\\
        X_0 & = & x_0
      \end{array}\right. \label{eq:sde-ou}
    \end{equation}
    where $\alpha, \sigma$ are positive constant and $\beta, x_0 \in
    \mathbb{R}$. Find the explicit solution to the SDE~{\eqref{eq:sde-ou}}.
    
    \item Prove that $X_t$ converges in distribution as $t \rightarrow \infty$
    to a Gaussian random variable with mean $\beta / \alpha$ and variance
    $\sigma^2 / 2 \alpha$.
  \end{enumeratealpha}
\end{exercise}

\

\begin{exercise}
  [Pts 3+2+2] Let $(B_t)_{t \geqslant 0}$ be a 2-dimensional Brownian motion
  and $X$ a two-dimensional stochastic process solution to the SDE
  \begin{equation}
    \left\{\begin{array}{lll}
      \mathd X_t & = & A X_t \mathd t + \mathd B_t \qquad t \geqslant 0\\
      X_0 & = & \xi
    \end{array}\right. \label{eq:sde-ou-twodim}
  \end{equation}
  where $\xi$ is a random variable in $\mathbb{R}^2$ independent of $B$ and
  \[ A = \left(\begin{array}{cc}
       \alpha & 1\\
       0 & \alpha
     \end{array}\right) \]
  with $\alpha \in \mathbb{R}$.
  \begin{enumeratealpha}
    \item Let $\phi (t)$ be a $2 \times 2$ matrix that satisfies the ODE
    \[ \dot{\phi} (t) = A \phi (t), \qquad \phi (0) =\mathbb{I}_2 \]
    where $\mathbb{I}_2$ is the $2 \times 2$ identity matrix. Show that $\phi
    (t) = e^{A t} = \sum_{n \geqslant 0} A^n \frac{t^n}{n!}$ and calculate
    $\phi (t)$ explicitly. Find $\phi (t)^{- 1}$ (inverse matrix).
    
    \item Verify that
    \[ X_t = \phi (t) \left( \xi + \int_0^t \phi (s)^{- 1} \mathd B_s \right)
    \]
    solves the SDE~{\eqref{eq:sde-ou-twodim}}.
    
    \item Calculate the explicit solution of~{\eqref{eq:sde-ou-twodim}}.
  \end{enumeratealpha}
\end{exercise}

\

\hrulefill

\

\end{document}
